Planetary perturbers: Flaring star-planet interactions in Kepler and TESS

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

>>>>

\section{Flaring finding in Kepler and TESS: False positives}

\begin{figure*}
    \script{paper_false_positives.py}
    \includegraphics[width=\linewidth]{figures/systematics_false_positives.png}
    \caption{\textcolor{red}{False positive flare candidates in Kepler and TESS light curves. \textbf{Left panel}: Kepler-235 with a possible argabrightening in the 1-min cadence light curve in  Quarter 14. Argabrightenings are few-minutes long reflections of light off debris and onto the detector~\citep{vancleve2016kepler}. The reflections affect large parts of the detector, so that this event can be identified as a false positive by its common occurrence across many light curves. \textbf{Right panel:} K2-77 with a Solar System Object (SSO) moving across the TESS detector in the 2-min cadence light curve in Sector 44. SSOs produce smooth and nearly symmetrical brightenings as they move in and out of the aperture of the star. They can also (partially) be identified with known SSOs~\citep{berthier2006skybot, berthier2016prediction}.}}
\end{figure*}
